\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change

### 2014-10-27 manuscript/ms_MicroMeso.Rnw
little update for saving 1000 iterations for model

\subsection{Computing}
\subsubsection{Model fitting}
All of our analyses (model selection, fitting, and simulating) were conducted in R. We used the analytical Bayesian software INLA to fit candidate vital rate models at the individual and quadrat levels for computational efficiency. This is the case except for the recruitment model at the individual level which required a more complex hierarchical approach. In that case we used the MCMC sampler in JAGS to estimate the posterior distributions of model parameters. After model selection, we used MCMC samplers, again in JAGS, to estimate the posterior distributions of model parameters for all vital rate models at the individual and quadrat levels. We obtained posterior distributions for all model parameters from three MCMC chains run for 10,000 iterations, after discarding the initial 5,000 iterations. We assessed convergence visually and using the Gelman diagnostic in the R package `coda.'

>>>>

\subsection{Computing}
\subsubsection{Model fitting}
All of our analyses (model selection, fitting, and simulating) were conducted in R. We used the analytical Bayesian software INLA to fit candidate vital rate models at the individual and quadrat levels for computational efficiency. This is the case except for the recruitment model at the individual level which required a more complex hierarchical approach. In that case we used the MCMC sampler in JAGS to estimate the posterior distributions of model parameters. After model selection, we used MCMC samplers, again in JAGS, to estimate the posterior distributions of model parameters for all vital rate models at the individual and quadrat levels. We obtained posterior distributions for all model parameters from three parallel MCMC chains run for 20,000 iterations, after discarding the initial 10,000 iterations. We assessed convergence visually and using the Gelman diagnostic in the R package `coda.' Scale reduction factors for all parameters were less than 1.02, indicating convergence. For the purposes of introducing stochasticity in our population models, we saved the final 1,000 iterations from each chain for all parameters to be used as randomly drawn values during population simulation.
